Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Add comment
Fix syntax error
Sate, that Doctest and Hspec miss some features

Automation, such as test discovery and continuous integration (CI)
~\cite{ci} is an important aspect of BDD.

Our contributions are:

>>>>

\begin{quote}
    \emph{sol: @mkl, any idea where to put this?}

\emph{Automation, such as test discovery and continuous integration (CI)
~\cite{ci} is an important aspect of BDD.}
\end{quote}

Both, Doctest and Hspec miss some features.  So we extend them as
needed.  Our contributions are:
